\sysfull

### 2019-09-13 paper/TOSN/intro.tex
update figure and add reference

\paragraph{Drawbacks of Static Task Decomposition.}
Task-based programming and execution models require a programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to statically decompose a program into a collection of tasks. \emph{Tasks}, top-level functions, can include arbitrary computation that should be executed despite arbitrarily-timed power failures. The programmer (or a compiler) explicitly expresses task-to-task control flow. Fig.~\ref{fig:coalesce} (left) illustrates how a program's tasks execute and shows how task transitions can affect run time. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at run-time. A programmer may thus create very large tasks in an attempt to reduce task transitions overhead. However, a large task may require more energy to complete than a device's fixed hardware energy buffer can hold, which may lead to a task \emph{non-termination} problem (Fig.~\ref{fig:coalesce}, right). To eliminate this risk, existing systems require the programmer to decompose a program into small tasks to preserve execution progress. These constraints on task sizing lead to the following \emph{dilemma}: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete but incur a high task transition and commit overhead?

>>>>

\paragraph{Drawbacks of Static Task Decomposition.}
Task-based programming and execution models require a programmer~\cite{alpaca,chain,patoukas2018feasibility} or a compiler~\cite{baghsorkhi_cgo_2018} to statically decompose a program into a collection of tasks. \emph{Tasks}, top-level functions, can include arbitrary computation that should be executed despite arbitrarily-timed power failures. The programmer (or a compiler) explicitly expresses task-to-task control flow. Fig.~\ref{fig:coalesce} (left) illustrates how a program's tasks execute and shows how task transitions can affect run time. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at run-time. A programmer may thus create very large tasks in an attempt to reduce task transitions overhead. However, a large task may require more energy to complete than a device's fixed hardware energy buffer can hold, which may lead to a task \emph{non-termination} problem (Fig.~\ref{fig:coalesce}, right). To eliminate this risk, existing systems require the programmer to decompose a program into small tasks to preserve execution progress. These constraints on task sizing lead to the following \emph{dilemma}: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete but incur a high task transition and commit overhead?
